\documentclass{beamer}
\usepackage{mathtools}
% \usepackage{color}
% \usepackage{pgfpages}
% \pgfpagesuselayout{4 on 1}[a4paper, border shrink=5mm, landscape]

% \usepackage{listings}
% \usepackage{minted}
% \usetheme{Madrid}
% \usetheme{Boadilla}
% \usetheme{Warsaw}
% \usetheme{Bergen}
% \usetheme{Amsterdam}
\usetheme{default}
\usecolortheme{beaver}
% \usepackage[number]{natbib}
\usepackage{natbib}


\title[CP]{L5DC Computing Project}
\subtitle{Project proposal}
\author{Achyut Timsina}

\date{\today}
\institute[Softwarica]{Softwarica college of IT \& E-Commerce\\
Kathmandu, Nepal\\
\url{achyut@gmail.com}
}
\begin{document}

\maketitle


\section{Computing project introduction} % (fold)
\label{sec:computing_project_introduction}

% \begin{frame}[t]\frametitle{Computing project's importance}
% \begin{itemize}
%     \item Culmination of two years of education
%     \item 
%     \item Your selling point for the rest of your life!
%     \item 
% \end{itemize}
% \end{frame}

\begin{frame}[t]\frametitle{Tasks overview}
The project is divided into a number of sub-task as follows:
\begin{enumerate}
    \item Project proposal
    \item Analysis specification
    \item Design specification
    \item Midway presentations
    \item Final report
    \item Final presentation/demonstration
\end{enumerate}
\end{frame}

\begin{frame}[t]\frametitle{Assignment rules}
\begin{itemize}
    \item All reports (doc/pdf) should be named as batch\_firstName\_lastName\_taskName\_version, For example: 9\_ram\_shrestha\_proposal.pdf(doc)
    \item Plagiarism will not be tolerated, and you have to submit your report to \url{www.turnitin.com} for the plagiarism check!
    \item Use Harvard style for referencing.
    \item All assignments hard copy and soft copy should be submitted with in respective deadlines.
    \item The deadlines are strict!
    \item The deadlines are published at computing project's site.
    \item Failure to submit assignments on the published deadlines will result in failing the course!
    \item Goal is to make you working continuously towards completion of projects on time with vibrant results!
    \item Email address for all of your digital communications is \textbf{cpsoftwarica@gmail.com}. I will try to write back with in 24 hours.
\end{itemize}
\end{frame}
% section computing_project_introduction (end)

\input{proposal}

% bibliography
\begin{frame}[t]\frametitle{References}
\cite{dawson2005projects}, \cite{weaver2004success}

\bibliography{../bib_files/cp}
\bibliographystyle{plainnat}
\end{frame}

\end{document}
