%!TEX root = final_report.tex
\chapter{Implementation} % (fold)
\label{cha:implementation}
This chapter should discuss:
\begin{itemize}
  \item Choice of programming language
  \item System cut-over from the development architecture to the implementation architecture
  \item Data migration from the development architecture and/or existing systems to the implementation architecture
  \item Training (how, why and when particular groups of users will use the user guides?)
\end{itemize}

\section{Programming language(s)} % (fold)
\label{sec:programming_languages}
Which programming language you have used to develop your application?
Why you have chosen that particular language?
Given detailed description of the particular programming language, including historical background, current development, recent features, language usage context, etc. (Research and write).
% section programming_languages (end)

\section{Development environment} % (fold)
\label{sec:development_environment}
You should write about:
\begin{itemize}
  \item Standard libraries
  \item IDEs
  \item Frameworks (testing frameworks, etc.)
  \item Your development platform
  \item Other CASE / design tools you have used
\end{itemize}
% section development_environment (end)

\section{Deployment strategy} % (fold)
\label{sec:deployment_strategy}
You should describe:
\begin{itemize}
   \item System migration from development environment to production environment
   \item Data migration from development environment from development environment to production environment
   \item Can be shown using deployment diagram
 \end{itemize}
% section deployment_strategy (end)

\section{User training} % (fold)
\label{sec:user_training}

This involves the development of user guide that should be placed in the appendix. The user guide should consist of screen dumps of the system along with supportive narrative that explains how to use a particular screen. There should be a short section in the report that explains how, why and when particular groups of users will be trained.
% section user_training (end)

\section{Conclusion} % (fold)
Summarize the things you have done in this chapter.
% section conclusion (end)
% chapter implementation (end)
