%!TEX root = final_report.tex
\chapter{Introduction} % (fold)
\label{cha:introduction}

This chapter should provide:
\begin{itemize}
  \item Brief, relevant background to the system

  \item Justification for your project (Why it matters?)

  \item If any external agency is involved you should explain what the agency is, why the project is required and any other background.

  \item The system developed (Provide overview of your project, most probably with a rich picture.)
  \item The solution that emerged (For example: The final solution was developed using PHP and MySQL and implemented on the third party web server.)
  \item List of main features that your project has
  \item A short overview of the remaining chapters
  \item Rich picture and/or overview diagram(s) of your application
\end{itemize}

\section{Aims} % (fold)
\label{sec:aims}
State two or three major goals/aims of your project.
for example:\\
\begin{itemize}
  \item To build desktop application for managing student information of ABC college
  \item To automate the student information managing process in ABC college
\end{itemize}
% section aims (end)

\section{Objectives} % (fold)
\label{sec:objectives}

Objectives are the set of activities that you perform to achieve the stated aims. Your objectives should be SMART.

Some of the objectives will be technical(for instance, to solve some technical problem) and some will be personal (for instance, to learn a new programming language), and some academic (for instance, to learn different approaches to research activities).

State the objectives that you will have to perform to achieve the stated aim. For example:
\begin{itemize}
  \item To gather requirements from the stakeholders
  \item To design ...
  \item To develop ...
  \item To test ...
  \item To document ...
  \item etc.
\end{itemize}
% section objectives (end)

\section{Development methods} % (fold)
\label{sec:development_methods}
Describe which development method you choose and why?

Refer to NCC lecture notes for available types of software development methods. Choose either object-oriented waterfall or agile (iterative) development methodology.

List the reasons for selecting appropriate software development lifecycle model in your project.
% section development_methods (end)