%!TEX root = final_report.tex
\chapter{Other project issues} % (fold)
\label{cha:others}
You should provide the reflection on your project works till now.

\section{Project management} % (fold)
\label{sec:project_management}
You should discuss what are deviations between proposed and actual project schedule. The identified deviations with an appropriate reason for such deviation should be explained in this section in detail here.
% section project_management (end)

\section{Risk management} % (fold)
\label{sec:risk_management}
You should compare the proposed risks with actual risks and find out deviations and/or similarities between them. In case of deviations, you should provide appropriate reason(s) for such deviation in your risk plan.
% section risk_management (end)
\section{Configuration management} % (fold)
\label{sec:configuration_management}
This section should provide overview of your configuration management approach and whether it worked or not (discuss).
% section configuration_management (end)

\section{Testing} % (fold)
\label{sec:testing}
This section should include:
\begin{itemize}
  \item Reasons for doing testing in computing projects
  \item Types of testing available
  \item Your choice of testing methods
\end{itemize}

\subsection{Unit testing} % (fold)
\label{sub:unit_testing}
Describe unit testing (should answer why, what , how unit testing is done?)
Describe your choice of testing framework (if you have used any) For example PHPUnit or JUnit
% subsection unit_testing (end)

\subsection{Integration testing} % (fold)
\label{sub:integration_testing}
Describe integration testing (should answer why, what, how integration testing is done?)

List a sample integration test case suitable for your project as shown in the student's guide for the computing project.

You should put your actual test script in the appendix of this report.
% subsection integration_testing (end)
% section testing (end)
% chapter others (end)